Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
reduced two figures to only one
improved figure for branch-and-bound
abstract
conclusion

	\begin{abstract}	
		NEXT TRY
	\end{abstract}

@@

			\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw (a) -- (b) -- (c) -- (e) -- (a);
			\draw (f) -- (g) -- (c) -- (b) -- (f);
			\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
			\draw[fill=green, fill opacity=0.2] (a) -- (f) -- (g) -- (e) -- (a);
			\draw[fill=brown, fill opacity=0.2] (f) -- (g) -- (c) -- (b) -- (f);
			\node at (2.5, 4) {$P_0$};
			\node at (1, 1) {$P_1$};
			\node at (3.5, 1.5) {$P_2$};
		\end{tikzpicture}	
		\caption{Splitting of a search space into three subproblems and the possible candidates for solutions}
		\label{fig:branchAndBound}
	\end{figure}

@@

	\section{Conclusion}
	Constraint programming is a very useful tool in practice, as it can solve abritrary combinatorial or optimization problems. \emph{Gecode}, as representant of the various toolsets, implements a handy interface to transform a mathematical description of a problem into code, which then can be used to solve the problem. In conclusion, \emph{Gecode} provides all the necessary tools, combines them with a nice interface, and is still very flexible concering optimzation for a certain area through the possibility to implement custom search strategies, based on some well studied and efficient algorithms.

>>>>

	\begin{abstract}	
		Constraint programming is a way to describe and solve mathematical problems with arbitrary constraints. In the following paper I will explain the implemented algorithms in Gecode, a tool which can be used to solve problems through constraint programming.
	\end{abstract}

@@

			\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw (a) -- (b) -- (c) -- (e) -- (a);
			\draw (f) -- (g) -- (c) -- (b) -- (f);
			\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
			\draw[fill=green, fill opacity=0.2] (a) -- (f) -- (g) -- (e) -- (a);
			\draw[fill=brown, fill opacity=0.2] (f) -- (g) -- (c) -- (b) -- (f);
			\node at (2.75, 3.75) {$P_0$};
			\node at (1.25, 1.25) {$P_1$};
			\node at (3.75, 1.75) {$P_2$};
		\end{tikzpicture}	
		\caption{Splitting of a search space into three subproblems and the possible candidates for solutions}
		\label{fig:branchAndBound}
	\end{figure}

@@

	\section{Conclusion}
	\emph{Gecode}, as representant for an implemention of constraint programming, provides everything necessary to describe and solve arbitrary combinatorial or optimization problems. The interface allows an adaption to the specific area through modificiations of algorithms, restarts or the implementation of a custom search algorithm, based on the already provided ones. Therefore \emph{Gecode} can be used in various areas, starting from scheduling, over portfolio optimization up to technical problems like placement.
